---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
library(osmdata)
library(sf)
library(nominatimlite)
library(mapsf)
library(osrm)
library(geos)
```

# whereRthetrees

<img alt="" src="https://img.shields.io/badge/Intro_to_programming-Final_Project-green">
<img alt="" src="https://img.shields.io/badge/Made_with-%E2%99%A5_%26_R-pink">
<img alt="" src="https://img.shields.io/badge/Status-Done_and_dusted-%23C2E4EE">
<img alt="" src="https://img.shields.io/badge/This_is_about-%F0%9F%8C%B3-%23F5EEDA">

Being outside in nature is proven to be good for body and mind. It can be calming, relaxing and grounding. It can make one happy and more level-headed. So take a break, look for the closest public nature spot and go for a walk!

## Installation

You can install the development version of whereRthetrees from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sonjamaas/whereRthetrees")
```

## Example

This is a basic example which shows you how to use this package:

```{r example}
library(whereRthetrees)
whereRthetrees(8.671087, 52.113866, 200, 0)
```

Take a break from work and go hug a tree!
