---
title: "whereRthetrees"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{whereRthetrees}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::install_github("sonjamaas/whereRthetrees")
library(whereRthetrees)
```

# whereRthetrees

Being outside in nature is proven to be good for body and mind. It can be calming, relaxing and grounding. It can make one happy and more level-headed. So take a break, look for the closest public nature spot and go for a walk!

## Installation

You can install the development version of whereRthetrees from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sonjamaas/whereRthetrees")
```

## Example

This basic example shows you how to use this package:

```{r example}
library(whereRthetrees)
whereRthetrees(8.671087, 52.113866, 200)
```

Watch out, that this package uses the "car" profile from OSRM to calculate the closest point and belonging route. Therefore there might be a gap between your position and the start of the route, because cars can not go everywhere. There also might be a nature area that is closer to you, than the one displayed, that is reachable by foot or bike. To get the according map, please build a OSM-Server and change the profile in the findNature() function.

Take a break from work and go hug a tree!
